\section{The HHL Algorithm}
The next section will give a more detailed walkthrough of the HHL algorithm.
Thereby, it will go through all 5 phases namely, state preparation, quantum phase estimation, inversion of eigenvalues, inverse quantum phase estimation and lastly the measurement.

\subsection{State Preparation}

In total, we have $n_b + n + 1$ qubits. 
In the beginning, they are all initialized in their zero states as
\begin{equation}
\begin{split}
\ket{\Psi_0} &= \ket{0\dots0}_b\ \ket{0\dots0}_c\ \ket{0}_a \\
&= \ket{0}_b^{{\otimes n_b}}\ \ket{0}_c^{\otimes b}\ \ket{0}_a 
\end{split}
\end{equation}
We now have to load the vector $\vec{b}$ into the b-register. 
This is achieved by amplitude encoding
\begin{equation}
    \vec{b} = \begin{pmatrix} b_0\\ \vdots \\ b_{N-1} \end{pmatrix} 
    \Leftrightarrow  
     %b_0 \ket{0} + b_1 \ket{1} + \dots + b_{N-1} \ket{N-1}= \ket{b} \\
     \ket b = \sum_{i=0}^{N-1} b_i \ket i
\end{equation}

Thus, $\ket b$ is loaded into the b-register as such

\begin{equation}
\ket{\Psi_1} = \ket{b}_b\ \ket{0\dots0}_c\ \ket{0}_a
\end{equation}

We have successfully encoded the $\vec{b}$ into our b-register. 
We now continue with the QPE. 

\subsection{Quantum Phase Estimation}
We will only briefly go through the specifics of the QPE and will not discuss each step in detail, as this is not the main topic of this paper. 
For further explanations refer to this paper.
Todo

As already mentioned, the QPE is a procedure to evaluate an estimate of eigenvalues. 
It consists of three phases namely, creating superpositions of the clock-bits via Hadamard gates, controlled rotation via the unitary U and the IQFT.
After QPE we will have an estimate of the eigenvalues of the unitary $U$. 
As we have encoded $A$ as a Hamiltonian $U = e^{iAt}$, the phase of the eigenvalue of U is proportional to the eigenvalue of $A$.
We have to define a scaled version of our eigenvalues $\lambda_j$.
\begin{equation}
\widetilde{\lambda_j} = \frac {N\lambda_jt}{2\pi}
\end{equation}
where $t$ can be choosen freely so that the scaled eigenvalues $\widetilde{\lambda_j}$ are integers.

Thus, the eigenvalues of $A$ will be stored in the c-register after QPE as
\begin{equation}
\begin{split}
\ket{\Psi_2} &= \ket{b}_b \ket{\widetilde{\lambda}}_c\ket{0}_a \\
% &=\left(-\frac{1}{\sqrt{2}} \ket{u_0} \ket{01} +\frac{1}{\sqrt{2}}  \ket{u_1} \ket{10} \right)  \ket{0}_a\\
& =\sum_{j=0}^{N-1} b_j \ket{u_j}_b \ket{\widetilde{\lambda_j}}_c \ket 0_a
\end{split}
\end{equation}
Notice, that the b-register is in the same form as we have discussed in the previous section. 
The b-register represents the $\ket b$ state in the eigenbasis $\ket{u_j}$ of $A$ like this
\begin{equation}
\ket{b} = \sum_{j=0}^{N-1} b_j\ket{u_j}
\end{equation}

Now that we have achieved the eigenvalues and have represented our $\ket{b}$ in the eigenbasis of $A$, we invert the eigenvalues $u_i$.


\subsection{Inversion of the eigenvalues}
In the next step, we invert the eigenvalues.
This is achieved by the rotation of the ancilla qubit in the a-register by the eigenvalues in the c-register.
The state of the registers after the rotation looks like this

\begin{equation}
\ket{\Psi_3} = \sum_{j=0}^{N-1} b_j \ket{u_j}_b {\ket{\widetilde{\lambda_j}}}_c \left(\sqrt{1-\frac{C^2}{\widetilde{\lambda_j^2}}}\ket{0}_a + \frac{C}{\widetilde{\lambda_j}} \ket{1}_a\right)
\end{equation}

where $C$ is a constant that should be chosen to be as large as possible to increase the success probability.
Currently, the state of the a-register can either collapse into $\ket 1$ or $\ket 0$. 
The probability of the a-register collapsing to $\ket 1$ is $\left|\frac C {\widetilde{\lambda_j}}\right|^2$.
If the ancilla qubit collapses to $\ket 0$, the whole procedure has to be repeated from the beginning. 
As mentioned earlier this has to be done, because the rotation process is not unitary and has a probability to fail.

We assume that our rotation process was successful and the ancilla bit collapses to $\ket 1$. 
The registers will look as such
\begin{equation}
\ket{\Psi_4}= \frac {1} {\sqrt{\sum_{j=0}^{N-1}   \left|  \frac{b_jC} {\widetilde{\lambda_j}}\right|^2   }} 
\sum_{j=0}^{N-1} b_j \ket{u_j}_b \ket{\widetilde{\lambda_j}}_c \frac{C}{\widetilde{\lambda_j}} \ket1_a
\end{equation}

Note that term in front of the sum is just a factor to normalize the state. 
Let's call this normalization factor $D$.
We see that we now have a term $\frac{C}{\widetilde{\lambda_j}}$ that represents the inverted eigenvalues. 
This term can be moved freely as it is just a scalar,  such that the scalar is applied to the b-register
\begin{equation}
\ket{\Psi_4}= D
\sum_{j=0}^{N-1} \frac{C}{\widetilde{\lambda_j}} b_j \ket{u_j}_b \ket{\widetilde{\lambda_j}}_c \ket1_a
\end{equation}

If we go back to our idea from the mathematical overview section, our b-register is in the same form as our solution state
\begin{equation}
\ket{x} = \sum_{i=0}^{N-1} \lambda_i^{-1} b_j\ket{u_j}\\
\end{equation}

That means our solution is already encoded in our registers. 
The problem here is, that we cannot read the solution out yet.
This has to do with the states in the b-register and c-register being entangled with each other. 
That means, we cannot convert the b-register into a $\ket0 / \ket 1$ measurement.
In the following, we have to undo all operations to unentangle the state in the b-register and c-register, to achieve the correct result.

\subsection{Inverse Quantum Phase estimation.}
The unentangling of the registers is achieved through the IQPE which backtracks all calculations of the QPE.
We are left with the following state

\begin{equation}
\begin{split}
\ket{\Psi_5} &= \frac {1} {\sqrt{\sum_{j=0}^{N-1} \left| \frac{b_jC} {\lambda_j}\right|^2}}
\sum_{j=0}^{N-1}\frac{ C}{\lambda_j}   b_j \ket{u_j}_b \ket{0}_c^{\otimes n} \ket{1}_a\\
&= \frac {C} {\sqrt{\sum_{j=0}^{2^{n_b}-1} \left| \frac{b_jC} {\lambda_j}\right|^2}}
\ket{x}_b \ket{0}^{\otimes n}_c \ket{1}_a
\end{split}
\end{equation}

The a-register is untouched and still holds the $\ket 1$ state as before. 
The c-register however is reset to the zero state $\ket{0}^{\otimes n}_c$ as in the beginning of the process at $\ket {\Psi_0}$. 
It is now unentangled from the b-register.
The b-register now contains the solution $\ket x$ after the uncomputation and can be measured correctly.

We can furthermore simplify the term as we assume that  $C$ is real and that the eigenvectors $\ket{u_i}$, and the $\ket b$ state are normalized.
Then we can simplify it to

\begin{equation}
\begin{split}
\ket{\Psi_5} &= \frac {1} {\sqrt{\sum_{j=0}^{N-1} \left| \frac{b_j} {\lambda_j}\right|^2}}
\ket{x}_b \ket{0}^{\otimes n}_c \ket{1}_a\\
&= \ket{x}_b \ket{0}^{\otimes n}_c \ket{1}_a
\end{split}
\end{equation}

We can now read out the result $\ket x$ in the b-register.

\subsection{Measurement}
As mentioned earlier, we cannot obtain the whole solution for the $\vec x$ as reading out all the entries would cost us $\mathcal{O}(N)$ steps.
This would omit our speedup of $\mathcal{O}(log N)$. 
That means, by measuring we will only obtain an estimate of specific features of $\ket x$.
Using a linear operator $M$ we can perform various measurements on $\ket x$ by calculating the inner product as such
\begin{equation}
    \bra x M \ket x
\end{equation}
With this we can extract various statistical features of $\ket x$ like the norm of the vector, the average of the weight of the components, moments, probability distributions, localization and concentration in specific regions, etc.


























