\section{Quantum mechanical concepts}
In this section, we will discuss some basic quantum mechanical concepts. 

\subsection{Hermitian matrix}
A Hermitian matrix is a matrix, which is equal to its adjoint matrix. 
The matrix contains complex numbers and is the same after transposing and taking the complex conjugate of itself. 
Thus, a hermitian matrix $A^\dagger$ is defined as such
\begin{equation}
 A = \overline{A^T} \ = A^\dagger
\end{equation}
For example the following matrix is Hermitian:
\begin{equation}
\begin{split}
A &= \begin{bmatrix} 2 & 1-i \\ 1+i & 3 \\ \end{bmatrix} \\
\overline A &= \begin{bmatrix} 2 & 1+i \\ 1-i & 3 \\ \end{bmatrix}\\
\overline{A^T} &= \begin{bmatrix} 2 & 1-i \\ 1+i & 3 \\ \end{bmatrix} = A\\
\Rightarrow A &= \overline{A^T} = A^\dagger
\end{split}
\end{equation}
Hermitian matrices are important as we can easily encode them into our quantum system. 
More details will follow in the subsection for the types of encoding.

\subsection{Spectral Decomposition}
Lets say we have a Matrix A that we can diagonalize. 
Then we can describe it by its spectrum which is a matrix with the eigenvalues in the diagonal.
\begin{equation} 
A =  U D U^{\dagger} = \begin{pmatrix} U_1 & \dots & U_n \end{pmatrix} \begin{pmatrix} \lambda_1 & 0 & 0 \\  0 & \ddots & 0\\ 0 & 0& \lambda_n \\ \end{pmatrix} \begin{pmatrix} U^\dagger_1 \\ \vdots \\ U^\dagger_n \end{pmatrix}
\end{equation}
where $D$ is the diagonal matrix consisting of the eigenvalues and U consisting of eigenvectors of $A$.
With this, we can describe a matrix only by its eigenvectors and eigenvalues. 
Classically calculating the diagonal matrice of eigenvalues is slow, in comparison to the quantum version. 
As we will see, this will play a big role in our computation. 

\subsection{Types of Encoding}
Here we will discuss three common kinds of encodings namely, Hamiltonian encoding, Basis encoding and Amplitude encoding.

\subsubsection{Hamiltonian Encoding}
One type of Hamiltonian encoding is to encode a matrix into a unitary gate which can be implemented into logical quantum gates. 
That means we can encode a matrix $A$ into our quatum system.
For example, a possible unitary gate of the matrix $A$ is
\begin{equation}
    U = e^{iAt}
\end{equation}
if $A$ is a Hermitian matrix.

\subsubsection{Basis Encoding}
Basis encoding converts classical numbers into quantum state, by using the binary representation of a number, we can directly write it into our quantum state. 
\begin{equation}
    x \rightarrow \ket {x}
\end{equation}
where $x$ is our binary number.
Lets say $x=3$ is our decimal number and can be represented as a binary number as such $x_b = 11$.
Then we can encode it in our quantum state as such
\begin{equation}
    x=2 \xrightarrow[]{binary} x_b = 10 \xrightarrow[]{quantum\  state} \ket{x_b} = \ket{10}
\end{equation}

\subsubsection{Amplitude Encoding}
Amplitude encoding encodes a vector $\vec x$ into a quantum state $\ket x$. 
We assume, that the vector $\vec x$ is normalized. 
Then we can use the elements of the vector $\vec x$ as coefficients of the states $\ket 0 \dots \ket {N-1}$ as such
\begin{equation}
    \vec{x} = \begin{pmatrix} x_0\\ \vdots \\ x_{N-1} \end{pmatrix} 
    \Leftrightarrow  
     \ket x = \sum_{i=0}^{N-1} x_i \ket i
\end{equation}

\subsection{Kronecker Delta}
The Kronecker delta $\delta_{ij}$ is often used to simplify calculations with inner product $\braket{\psi | \phi}$.
Basically, $\psi$ and $\phi$ can be handeled like normal vectors. 
The inner product can calculate the angle between vectors, which means that for two orthogonal kets the inner product is $0$ as such
\begin{equation}
\braket{\psi|\phi} = 1
\end{equation}
Lets say we have an orthonormal basis $\ket{E_i}$, meaning all basis vectors are orthonormal to each other, then we have the following relation
\begin{equation}
\begin{split}
\braket{E_i|E_i} &= 1\\
\braket{E_i|E_j} &= 0, \ i\neq j
\end{split}
\end{equation}

We can see that if the indices are the same, which means the vectors are pointing into the same direction, the inner product is $1$.
If they are orthogonal to each other, which means every other vector in an orthonormal basis, then the inner product is $0$.
This can be summarized in the Kronecker delta
\begin{equation}
    \delta_{ij} = \braket{E_i|E_j} = \begin{cases} 1 & \text{if } i=j\\ 0 & \text{if } i \neq j
\end{cases}
\end{equation}
This can quite usefull in calculations with orthonormal basises
When calculating inner product of an orthonormal basis, whilst the indices are not equal, terms can be multiplied by $0$ and will be cancel out, simplifying the equation.

\subsection{Etangled states}
Entangled states can not be represented by a tensor product of individual states. 
Entangled states are defined as such
\begin{equation}
    \ket{\Phi} \neq \ket{\phi} \ket{\psi}
\end{equation}
As an example here we have a state $\ket{Psi_1}$ which is not entangled, as we can represent it by two other states
\begin{equation}
\begin{split}
\ket{\Phi_1} &= \frac{1}{\sqrt{2}} ( \ket{10} + \ket{11}) \\ 
&= \ket{1}\otimes \frac{1}{\sqrt{2}} ( \ket{0} + \ket{1})\\ 
&= \ket{1} \ket{+}
\end{split}
\end{equation}
where $\ket +$ is the Hadmard  $H \ket{0}$.
On the other hand the following state $\Psi_2$ is entangled 
\begin{equation}
\begin{split}
\ket{\Phi_2} &= \frac{1}{\sqrt{2}} ( \ket{00} + \ket{11}) \\
&\neq \ket{\alpha}\ket{\beta}
\end{split}
\end{equation}
as it cannot be represented by other states.
