\begin{thebibliography}{00}

\bibitem{hhl} 
A. Harrow, A. Hassidim, and S. Lloyd, 
"Quantum algorithm for linear systems of equations," 
Phys. Rev. Lett. 103, 150502, 
2009.
[Online]. Available: \url{https://arxiv.org/abs/0811.3171} 

\bibitem{qiskit_hhl} 
Qiskit Community,  
"Solving Linear Systems of Equations using HHL and its Qiskit Implementation", 
[Online]. Available: 
\url{https://learn.qiskit.org/}\url{course/ch-applications}\url{/solving-linear-systems-of-equations-}\url{using-hhl-and-its-}
\url{qiskit-implementation},  
Accessed June 30, 
2023.

\bibitem{primer} 
D. Dervovic, M. Herbster, P. Mountney, S. Severini, N. Usher, L. Wossnig, 
"Quantum linear systems algorithms: a primer", 
2018.
[Online]. Available: \url{ https://arxiv.org/abs/1802.08227}

\bibitem{step_by_step} 
H. Morrell Jr, A. Zaman, H. Wong, 
"Step-by-Step HHL Algorithm Walkthrough to Enhance the Understanding of Critical Quantum Computing Concepts", 
2021.
[Online]. Available: \url{ https://arxiv.org/abs/2108.09004}

\bibitem{fineprint} 
S. Aaronson, 
"Read the fine print",  
Nature Phys 11, 291-293, 
2015.
[Online]. Available: \url{ https://inspirehep.net/literature/1834407}


\bibitem{electrical_networks} 
G. Wang, 
"Efficient Quantum Algorithms for Analyzing Large Sparse Electrical Networks",
Quantum Information \& Computation 17 (11 \& 12): 987-1026, 
2017. 
[Online]. Available: \url{ https://arxiv.org/abs/1311.1851}

\bibitem{data_fitting} 
N. Wiebe, D. Braun, S. Lloyd, 
""Quantum Data Fitting", 
Phys. Rev. Lett. 109, 050505, 
2012.
[Online]. Available: \url{ https://arxiv.org/abs/1204.5242}

\bibitem{without_ancilla} 
D. V. Babukhin, 
"Harrow-Hassidim-Lloyd algorithm without ancilla postselection",
Dukhov Research Institute of Automatics (VNIIA), 127055 Moscow, Russia,
2022.
[Online]. Available: \url{ https://arxiv.org/abs/2208.02200}

\bibitem{qram}
Quantum random access memory,
Vittorio Giovannetti1, Seth Lloyd2, Lorenzo Maccone3,
V. Giovannetti, S. Lloyd, L. Maccone, Phys. Rev. Lett. 100, 160501,
2008.
[Online]. Available: \url{ https://arxiv.org/abs/0708.1879}


\end{thebibliography}



\begin{comment}
- Qram

it-sec:
- larg scale linear systems
- pattern recognitionj

    HHL-2009: 
    step by step: 
    primer: https://arxiv.org/abs/1802.08227
    exponential imprved dependencs on precision: https://arxiv.org/abs/1511.02306
    without ancilla: 
    data fitting:
    fineprint: 
    large electrical networks: 
    qiskit example: https://learn.qiskit.org/course/ch-applications/solving-linear-systems-of-equations-using-hhl-and-its-qiskit-implementation#example1


    QPE: https://arxiv.org/abs/quant-ph/9511026
\end{comment}
